---
title: "Knapsack Problem"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab_report_knapsack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lab6group8)
```
## Introduction
The knapsack problem or rucksack problem is a problem in combinatorial optimization: Given a set of items, each with a weight and a value, determine the number of each item to include in a collection so that the total weight is less than or equal to a given limit and the total value is as large as possible.

This package contains 3 different algorithms to solve the knapsack problem:  
1. `brute_force_knapsack`  
2. `dynamic_knapsack`  
3. `greedy_knapsack`  

The inputs of the function are:  
`x`: A `data.frame` consisting of two variables. `w` represents the object's weight and `v` is the value.  
`W`: the maximum capacity of the knapsack.  
In the `brute_force_knapsack`, there's one additional argument `parallel` that's set to `FALSE` by default. If `TRUE`, the function is parallelized over detected cores.  

We generate the data to run examples as below:
```{r}
suppressWarnings(RNGversion("3.5.9"))
set.seed(42)
n <- 2000
knapsack_objects <- data.frame(
  w=sample(1:4000, size = n, replace = TRUE),
  v=runif(n = n, 0, 10000)
)
```

## brute_force_knapsack
This function returns the maximum value given the capacity of knapsack by looking through every possible alternatives.  
**example:**
```{r}
brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500)
```
**Question:** How much time does it takes to run the algorithm for n = 16 objects?
```{r}
system.time(brute_force_knapsack(x = knapsack_objects[1:16, ], W = 3500))
```


## dynamic_knapsack
This function returns the maximum value given the capacity of knapsack by using dynamic programming.
**example:**
```{r}
dynamic_knapsack(x = knapsack_objects[1:8,], W = 3500)
```
**Question:** How much time does it takes to run the algorithm for n = 500 objects?
```{r}
system.time(dynamic_knapsack(x = knapsack_objects[1:500,], W = 3500))
```


## greedy_knapsack
This function returns the maximum value given the capacity of knapsack by sorting the items in decreasing order of value per unit of weight.
**example:**
```{r}
greedy_knapsack(x = knapsack_objects[1:800,], W = 3500)
```
**Question:** How much time does it takes to run the algorithm for n = 1000000 objects?
```{r}
set.seed(42)
n <- 1000000
knapsack_objects <- data.frame(
  w=sample(1:4000, size = n, replace = TRUE),
  v=runif(n = n, 0, 10000)
)

system.time(greedy_knapsack(x = knapsack_objects, W = 3500))
```


## Parallelize brute_force_knapsack
**Question:** What performance gain could you get by parallelizing brute force search?  
The performance gained by parallelizing `brute_force_knapsack` is not significant when `x` has small number of rows (e.g., 8). However, when `x` has sufficiently large number of rows, (e.g., 22), the performance gain by parallelizing starts to show.

```{r, eval=FALSE}
system.time(brute_force_knapsack(knapsack_objects[1:22,], W = 3500))
system.time(brute_force_knapsack(knapsack_objects[1:22,], W = 3500, parallel = TRUE))
```
The estimated running time of the first line is about 52 seconds while the second line is about 34 seconds.